---
date: "2016-04-27T00:00:00Z"
external_link: ""
image:
  caption: Photo by rawpixel on Unsplash
  focal_point: Smart
links:
- icon: github
  icon_pack: fab
  name: My packages 
  url: https://github.com/Foha2001/tunisianfirms
#slides: example
summary: Package presentation.
tags:
title: My Packages
url_code: ""
url_pdf: ""
url_slides: ""
url_video: ""
toc: true
output:
  blogdown::html_page:
    toc: true
---
<style type="text/css">
h1 { /* Header 2 */
    font-size: 32px;
    color: DarkBlue;
    font-weight: bold;
}

h2 { /* Header 1 */
  font-size: 24px;
  color: #9d3ae8;
  font-weight: bold;
}
</style>



# 1- Tunisianfirms
The goal of tunisianfirms is to spread cotation of Tunisian stock Exchange Firms

## Installation
Coming soon You can install the released version of tunisianfirms from CRAN soon.
However, you can install from github with these 

```{r}
library(devtools)
devtools::install_github("Foha2001/tunisianfirms")
```
you have to install devtools before, when installing from github
call the package with :
```{r}
library(tunisianfirms)
```
## Examples 
basic example code

```{r}
cotation("ATTIJARIBANK")

```


To show a sample_example run


```{r}

head(sample_data)
```

# 2- fdesc
The goal of fdesc is to measure describtive statistics and export values into excel file in table format.

## Installation
You can install the development version of fdesc like so:
```{r}
library(devtools)
```

```{r}
#devtools::install_github("Foha2001/fdesc")
```

## Example

```{r}
library(fdesc)
```
To describe your database run this code \code{\link{desc}}
```{r}
mytable<- desc(data)
mytable
```

To export your Table to Excel format 

```{r}
export(mytable)
```
You will find your Excel table with the name descstatistics.xlsx





