---
date: "2016-04-27T00:00:00Z"
external_link: ""
image:
 # caption: Photo by rawpixel on Unsplash
  focal_point: Smart
links:
- icon: github
  icon_pack: fab
  name: 
  url: 
#slides: example
summary: Package presentation.
tags:
- Deep Learning
title: Risk Management blog 
url_code: ""
url_pdf: ""
url_slides: ""
url_video: ""
toc: true
output:
  blogdown::html_page:
    toc: true
---

<style type="text/css">

p1 {
  font-size: 12pt;
  font-weight: bold;
}


h1 { /* Header 2 */
    font-size: 32px;
    color: DarkBlue;
    font-weight: bold;
}

h2 { /* Header 1 */
  font-size: 24px;
  color: green;
  font-weight: bold;
}

h3 { /* Header 2 */
  font-size: 24px;
  color: #9d3ae8;
  font-weight: bold;
}



</style>

## Material Building packages code

To build package use these commands:
```{r}
 library(devtools)
 library(usethis) 
```
- usethis::use_r("nomdufichier") : to add R file and write function
- devtools::load_all()  : to load all related functions to yours
- devtools::install() : to install your package
- devtools::document()   : to document your package using roxygen
- usethis::create_package() : to directly create package
- usethis::use_git() : to use package version control vith github 
- devtools::load_all() :  to load all source functions to be able to test package
- devtools::check()	: to check our package
- use_data_raw() 	: create file to build data
- usethis::use_data(my data, compress="xz"):  to add data to my package
- use_package("add any package you need") : add any package to import from to description file


## build Normal distribution

```{r}
x <- seq(-4,4, length=1000)
hx <- dnorm(x,mean=0, sd=1)
plot(x, hx, type="l", xlab = "valeur de x", ylab="density", main="loi normale")
```

## function to create asymetric distribution
```{r}
fs = function(x,epsilon,delta) dnorm(sinh(delta*asinh(x)-epsilon))*delta*cosh(delta*asinh(x)-epsilon)/sqrt(1+x^2)
vec = seq(-5,5,0.001)
plot(vec,fs(vec,0,1),type="l")
points(vec,fs(vec,-2,1.3),type="l",col="red")
points(vec,fs(vec,1.3,1),type="l",col="blue")

```




